---
title: "Data Structures in R"
author: "Musa R. Nyakerabachi"
date: "1/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives.

This project is about building my skills of the data analysis workflow by evaluating the COVID_19 situation.

# Data exploration

```{r }
#loading data set
options(warn = -1)
install.packages("tidyverse")
install.packages("readr")
library(readr)
library(tidyverse)
df<-read.csv("covid19.csv")

head(df)
```


```{r}
#number of rows and columns
dim(df)

#viewing column names and storinh them in a variable
col_names<- colnames(df)

#install.packages("skimr") for skimming through the data set

#skimming through the data
library(skimr)
skim(df)
col_names

#viewing  and summarising data
glimpse(df)
```
From above analysis I have used ``tidyverse`` and ``skimr`` package to give all overview of the data set. The data set has 14 colums and 10903 rows. It has 5 columns with character and 9 columns with numeric. From above, the data has no missing values.The ``glimpse`` function also show an overview of the all columns but ``skim`` function from ``skimr`` package give more details than what ``glimpse`` function which is in the umbrella of a group of packages hold by ``tidyverse``.  
 
 
```{r}
#filter the ``all states`` province state and remove the Province_state column
covid_allsates <- df %>% filter(Province_State == "All States") %>% select(-Province_State)

```
 From above snippet of code we have removed one column and it consist only All state row.
```{r}

```

```{r}

```

```{r}

```

```{r}

```


```{r}

```


```{r}

```


```{r}

```

```{r}

```


```{r}

```